Modeling and analyzing the Corona-virus warning app with the Isabelle Infrastructure framework

### 2020-07-09 paper.tex
I've added the sections Model and Analysis (making them one section).

\newcommand{\symb}[1]{\makebox{\it #1}} 
\newcommand\ie{i.e.\!\,, }
\newcommand\rel{Re${\cal{L}}$}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand*{\TODOfn}[2][noteC]{\TODO[#1]{[\footnote{\TODO[#1]{#2}}]}}
\newcommand*{\TODOref}[2][todoC]{\TODOfn[#1]{\textbf{BIB-REF}: #2}}
\newcommand\ttand{\mbox{{$\land$}}}
\newcommand\ttor{\mbox{{$\lor$}}}
\newcommand\ttcap{\mbox{{$\cap$}}}
\newcommand\ttcup{\mbox{{$\cup$}}}
\newcommand\ttfun{\mbox{{$\Rightarrow$}}}
\newcommand\ttmimp{\mbox{{$\Longrightarrow$}}}
\newcommand\ttimp{\mbox{{$\longrightarrow$}}}
\newcommand\ttequiv{\mbox{{$\equiv$}}}
\newcommand\ttexists{\mbox{{$\exists$}}}
\newcommand\ttforall{\mbox{{$\forall$}}}
\newcommand\ttneg{\mbox{{$\neg$}}}
\newcommand\ttneq{\mbox{{$\neq$}}}
\newcommand\ttin{\mbox{{$\in$}}}
\newcommand\ttnin{\mbox{{$\notin$}}}
\newcommand\ttImp{\mbox{{$\Longrightarrow$}}}
\newcommand\ttlam{\mbox{\( \lambda \)}}
\newcommand\tttimes{\mbox{\( \times \)}}
\newcommand\ttlbrack{\mbox{\(\llbracket\)}}
\newcommand\ttrbrack{\mbox{\( \rrbracket \)}}
\newcommand\noie{\textit{i.e.},\xspace}
\newcommand\eg{~\textit{e.g.},\xspace}
\newcommand\noeg{\textit{e.g.},\xspace}
\newcommand\ttatI{\mbox{\( @_G \)}}
\newcommand\ttto[1]{\mbox{{$\to^{#1}$}}}
\newcommand\ttleq{\mbox{{$\le$}}}
\newcommand\ttrelI{\mbox{{$\to_{i}$}}}
\newcommand\ttrelIstar{\mbox{{$\to^*$}}}
\newcommand\ttrel[1]{\mbox{{$\to_{#1}$}}}
\newcommand\ttrelstar[1]{\mbox{{$\to_{#1}^*$}}}
\newcommand\ttalpha{\mbox{{$\alpha$}}}
\newcommand\ttsupseteq{\mbox{{$\supseteq$}}}
\newcommand\ttupdownarrow{\mbox{{$\Updownarrow$}}}
\newcommand\tttau{\mbox{{$\tau$}}}
\newcommand\ttsubseteq{\mbox{{$\subseteq$}}}
\newcommand\ttf{\mbox{{$f$}}}
\newcommand\ttvdash{\mbox{{$\vdash$}}}
\newcommand\ttref[1]{\mbox{\(\sqsubseteq_{#1}\)}}
\newcommand\ttNatt{\mbox{{$\mathcal{N}$}}}
\newcommand\ttattand[1]{\mbox{{$\oplus_{\wedge}^{#1}$}}}
\newcommand\ttattor[1]{\mbox{{$\oplus_{\vee}^{#1}$}}}
\newcommand\ttsigma{\mbox{{$\sigma$}}}
\newcommand\ttmref[1]{\mbox{{$\sqsubseteq_{#1}$}}}
\newcommand\ttmeref{\ttmref{\mathcal{E}}}
\newcommand\ttsn{\mbox{{\texttt{s}$_0$}}}
\newcommand\ttsigmap{\mbox{{$\sigma'$}}}
\newcommand\ttecal{\mbox{$\mathcal{E}$}}
\newcommand\ttimg{\mbox{$\triangleleft$}}

@@

\subsection{Isabelle Infrastructure framework}
\label{sec:isainf}
%\TODO{Adapt: this is copied from FMBC paper}
The Isabelle Infrastructure is built in the interactive generic theorem prover
Isabelle/HOL \cite{npw:02}. As a framework, it supports formalization and proof of
systems with actors and policies. It originally emerged from verification of insider 
threat scenarios but it soon became clear that the theoretical concepts, like temporal
logic combined with Kripke structures and a generic notion of state transitions were
very suitable to be combined with attack trees into a formal security engineering process
\cite{suc:16} and framework \cite{kam:19a}.

\subsubsection{Overview}
\label{sec:isainfover}
Figure \ref{fig:theorystruc} gives an overview of the Isabelle Infrastructure 
framework with its layers of object-logics -- each level below embeds the one
above showing the novel contribution of this paper in blue on the top. 
\begin{figure}
\begin{center}
  \includegraphics[scale=.5]{theory_structure.pdf}
\end{center}
%\vspace{-.5cm}
\caption{Generic Isabelle Infrastructure framework applied to Corona-warning app.}
\label{fig:theorystruc}
\end{figure}

@@

\section{Model}
\label{sec:model}

\section{Analysis}
\label{sec:ana}

@@

\section{Refining the Specification}
\label{sec:corref}

>>>>

\newcommand{\symb}[1]{\makebox{\it #1}} 
\newcommand\ie{i.e.\!\,, }
\newcommand\rel{Re${\cal{L}}$}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand*{\TODOfn}[2][noteC]{\TODO[#1]{[\footnote{\TODO[#1]{#2}}]}}
\newcommand*{\TODOref}[2][todoC]{\TODOfn[#1]{\textbf{BIB-REF}: #2}}
\newcommand\ttand{\mbox{{$\land$}}}
\newcommand\ttor{\mbox{{$\lor$}}}
\newcommand\ttcap{\mbox{{$\cap$}}}
\newcommand\ttcup{\mbox{{$\cup$}}}
\newcommand\ttfun{\mbox{{$\Rightarrow$}}}
\newcommand\ttmimp{\mbox{{$\Longrightarrow$}}}
\newcommand\ttimp{\mbox{{$\longrightarrow$}}}
\newcommand\ttequiv{\mbox{{$\equiv$}}}
\newcommand\ttexists{\mbox{{$\exists$}}}
\newcommand\ttforall{\mbox{{$\forall$}}}
\newcommand\ttneg{\mbox{{$\neg$}}}
\newcommand\ttneq{\mbox{{$\neq$}}}
\newcommand\ttin{\mbox{{$\in$}}}
\newcommand\ttnin{\mbox{{$\notin$}}}
\newcommand\ttImp{\mbox{{$\Longrightarrow$}}}
\newcommand\ttlam{\mbox{\( \lambda \)}}
\newcommand\tttimes{\mbox{\( \times \)}}
\newcommand\ttlbrack{\mbox{\(\llbracket\)}}
\newcommand\ttrbrack{\mbox{\( \rrbracket \)}}
\newcommand\noie{\textit{i.e.},\xspace}
\newcommand\eg{~\textit{e.g.},\xspace}
\newcommand\noeg{\textit{e.g.},\xspace}
\newcommand\ttatI{\mbox{\( @_G \)}}
\newcommand\ttto[1]{\mbox{{$\to^{#1}$}}}
\newcommand\ttleq{\mbox{{$\le$}}}
\newcommand\ttrelI{\mbox{{$\to_{i}$}}}
\newcommand\ttrelIstar{\mbox{{$\to^*$}}}
\newcommand\ttrel[1]{\mbox{{$\to_{#1}$}}}
\newcommand\ttrelstar[1]{\mbox{{$\to_{#1}^*$}}}
\newcommand\ttalpha{\mbox{{$\alpha$}}}
\newcommand\ttsupseteq{\mbox{{$\supseteq$}}}
\newcommand\ttupdownarrow{\mbox{{$\Updownarrow$}}}
\newcommand\ttbigcap{\mbox{{$\bigcap$}}}
\newcommand\tttau{\mbox{{$\tau$}}}
\newcommand\ttsubseteq{\mbox{{$\subseteq$}}}
\newcommand\ttf{\mbox{{$f$}}}
\newcommand\ttvdash{\mbox{{$\vdash$}}}
\newcommand\ttref[1]{\mbox{\(\sqsubseteq_{#1}\)}}
\newcommand\ttrefV{\mbox{{$\sqsubseteq_V$}}}
\newcommand{\ttcalN}[1]{\mbox{{${\mathcal{N}}_{\texttt{#1}}$}}} 
\newcommand\ttNatt{\mbox{{$\mathcal{N}$}}}
\newcommand\ttattand[1]{\mbox{{$\oplus_{\wedge}^{#1}$}}}
\newcommand\ttattor[1]{\mbox{{$\oplus_{\vee}^{#1}$}}}
\newcommand\ttsigma{\mbox{{$\sigma$}}}
\newcommand\ttmref[1]{\mbox{{$\sqsubseteq_{#1}$}}}
\newcommand\ttmeref{\ttmref{\mathcal{E}}}
\newcommand\ttsn{\mbox{{\texttt{s}$_0$}}}
\newcommand\ttsigmap{\mbox{{$\sigma'$}}}
\newcommand\ttecal{\mbox{$\mathcal{E}$}}
\newcommand\ttimg{\mbox{$\triangleleft$}}

@@

\subsection{Isabelle Infrastructure framework}
\label{sec:isainf}
%\TODO{Adapt: this is copied from FMBC paper}
The Isabelle Infrastructure is built in the interactive generic theorem prover
Isabelle/HOL \cite{npw:02}. As a framework, it supports formalization and proof of
systems with actors and policies. It originally emerged from verification of insider 
threat scenarios but it soon became clear that the theoretical concepts, like temporal
logic combined with Kripke structures and a generic notion of state transitions were
very suitable to be combined with attack trees into a formal security engineering process
\cite{suc:16} and framework \cite{kam:19a}.
%\subsubsection{Overview}
%\label{sec:isainfover}
Figure \ref{fig:theorystruc} gives an overview of the Isabelle Infrastructure 
framework with its layers of object-logics -- each level below embeds the one
above showing the novel contribution of this paper in blue on the top. 
\begin{figure}
\begin{center}
  \includegraphics[scale=.5]{theory_structure.pdf}
\end{center}
%\vspace{-.5cm}
\caption{Generic Isabelle Infrastructure framework applied to Corona-warning app.}
\label{fig:theorystruc}
\end{figure}

\subsubsection{Kripke structures, CTL, and Attack Trees}
\label{sec:intro}
The Isabelle framework has now after various case studies become a general framework for
the state-based security analysis of infrastructures with policies and actors. Temporal logic
and Kripke structures build the foundation. 
Meta-theoretical results have been established to show equivalence between attack trees 
and CTL statements \cite{kam:18b}. 
%As part of the meta-theory Correctness and Completeness have been 
%proved in Isabelle \cite{kam:18b} and can be used to navigate between CTL and attack 
%trees to find attacks. 
This foundation provides a generic notion of state transition on which attack trees and
temporal logic can be used to express properties. 
The main notions used in this paper are:
\begin{itemize}
\item {Kripke structures and state transitions:}\\ 
Using a generic state transition relation $\mapsto$, Kripke structures
are defined as a set of states reachable by $\mapsto$ from an initial
state set, for example
\begin{ttbox}
Kripke \{t. \ttexists i \ttin I. i \ttrelIstar t\} I
\end{ttbox} 
\item {CTL statements:}\\ 
For example, we can write 
\begin{ttbox}
K \ttvdash {\sf EF} s
\end{ttbox}
to express that in Kripke structure \texttt{K} there is a path on which
the property \texttt{s} (a set of states) will eventually hold.
\item {Attack trees:} \\
The datatype of attack trees has three constructors: 
$\oplus_\vee$ creates or-trees and $\oplus_\wedge$ creates 
and-trees.
And-attack trees $l \ttattand s$ and or-attack trees $l \ttattor s$ 
consist of a list of sub-attacks -- again attack trees. The third constructor 
creates a base attack as a pair of state sets written \texttt{\ttcalN{(I,s)}}.
For example, a two step and-attack leading from state set \texttt{I} via
\texttt{si} to \texttt{s} is expressed as
\begin{ttbox}
\ttvdash [\ttcalN{(I,si)},\ttcalN{(si,s)}]\ttattand{\texttt{(I,s)}}
\end{ttbox}
%\begin{ttbox}
%\ttvdash [\ttcalN{(I,s)},\ttcalN{(s,s')}]\ttattand{(I,s')}
%\end{ttbox}
\item {Attack tree refinement, validity and adequacy:}\\
Attack trees have their own refinement (not to be mixed up with the
system refinement presented in this paper as introduced in the next section).
An abstract attack tree may be refined by spelling out the attack steps until a valid attack
is reached:

\texttt{\ttvdash A :: (\ttsigma :: state) attree)}.

The validity is defined constructively (code is generated from it)
and its adequacy with respect to a formal semantics in CTL is proved
and can be used to facilitate actual application verification as demonstrated 
her in the stepwise system refinements.
\end{itemize}

@@

\section{Model for Corona-warning app}
\label{sec:model}

\subsection{Infrastructures, Policies, and Actors}
\label{sec:infra}
% Adapted from CSF paper
The Isabelle Infrastructure framework supports the representation of infrastructures 
as graphs with actors and policies attached to nodes. These infrastructures 
are the {\it states} of the Kripke structure. % for the attack trees.

The transition between states is triggered by non-parametrized
actions \texttt{get}, \texttt{move}, and \texttt{put} 
executed by actors. 
Actors are given by an abstract type \texttt{actor} and a function 
\texttt{Actor} that creates elements of that type from identities 
(of type \texttt{string} written \texttt{''s''} in Isabelle). 
Actors are contained in an infrastructure graph type \texttt{igraph}
constructed by its constructor \texttt{Lgraph}. 
\begin{ttbox}
{\bf datatype} igraph = 
         Lgraph (location \tttimes location)set 
                 location \ttfun identity set
                 identity \ttfun (string set \tttimes string set \tttimes efid)  
                 location \ttfun string \tttimes (dlm \tttimes data) set
                 location \ttfun efid set
                 actor \ttfun location \ttfun (identity \tttimes efid) set

\end{ttbox}
In the current application of the framework to the Corona-warning app case study, 
this graph contains a set of location pairs representing the %structure 
topology of the infrastructure
as a graph of nodes and a function%\footnote{ We use the common $\lambda$-abstraction, 
%e.g. \texttt{\ttlam x. True}, to define functions with parameters, here the 
%function returning True for any input $x$.} 
that assigns a set of actor identities to each node (location) in the graph.
The third component of an \texttt{igraph} assigns the credentials to each actor: 
a triple-valued function whose first range component is a set describing the credentials 
in the possession of an actor and the second component 
is a set defining the roles the actor can take on; 
most prominently the third component is the \texttt{efid} assigned to the actor. This is initially
just a natural number but will be refined to actually represent lists of ``Ephemeral'' Ids later
when refining the specification.
\begin{ttbox}
{\bf datatype} efid = Efid nat
\end{ttbox}
The fourth component of the type \texttt{igraph}
assigns security labelled data to locations, a feature not used in the
current application.
The second to last component assigns the set of efids of all currently present smart phones
to each location of the graph. The last component finally denotes the knowledge set of each
actor for each location: a set of pairs of actors and potential ids.

Corresponding projection functions for each of the components of an 
infrastructure graph are provided; they are named \texttt{gra} for the actual 
set of pairs of locations, \texttt{agra} for the actor map, \texttt{cgra} for 
the credentials, \texttt{lgra} for the %state of a location and the 
data at that location, \texttt{egra} for the assignment of current efids to locations,
and \texttt{kgra} for the knowledge set for each actor for each location.

In the Corona-virus warning app, the initial values for the \texttt{igraph} components use
two locations \texttt{pub} and \texttt{shop} to define the following constants (we omit the
data map component \texttt{ex\_locs}).
\begin{ttbox}
ex_loc_ass \ttequiv (\ttlam x. if x = pub then \{''Alice'', ''Bob'', ''Eve''\}  
                 else (if x = shop then \{''Charly'', ''David''\} 
                 else \{\}))
ex_creds \ttequiv (\ttlam x. if x = ''Alice'' then (\{\}, \{\}, Efid 1) else 
              (if x = ''Bob'' then  (\{\},\{\}, Efid 2) else 
              (if x = ''Charly'' then (\{\},\{\}, Efid 3) else
              (if x = ''David'' then (\{\},\{\}, Efid 4) else
              (if x = ''Eve'' then (\{\},\{\}, Efid 5)
               else (\{\},\{\},Efid 0))))))
ex_efids \ttequiv (\ttlam x. if x = pub then \{Efid 1, Efid 2, Efid 5\}
                  else (if x = shop then \{Efid 3, Efid 4\} else \{\}))
ex_knos \ttequiv (\ttlam x. (if x = Actor ''Eve'' then (\ttlam l. \{\} else (\ttlam l. \{\})))
\end{ttbox}  
These components are wrapped up into the following \texttt{igraph}.
\begin{ttbox}
ex_graph \ttequiv
      Lgraph \{(pub, shop)\} ex_loc_ass ex_creds ex_locs ex_efids ex_knos
\end{ttbox}  
Infrastructures are given by the following datatype that 
contains an infrastructure graph of type \texttt{igraph} 
and a policy given by a function that assigns local policies over a graph to
all locations of the graph. 
\begin{ttbox}
{\bf{datatype}} infrastructure = Infrastructure igraph 
                                         [igraph, location] \ttfun policy set
\end{ttbox}
There are projection functions \texttt{graphI} and \texttt{delta} when applied
to an infrastructure return the graph and the local policies, respectively.
The function \texttt{local\_policies} gives the policy for each location \texttt{x}
over an infrastructure graph \texttt{G} as a pair: the first element of this pair is 
a function specifying the actors \texttt{y} that are entitled to perform the actions 
specified in the set which is the second element of that pair.
The local policies definition for the Corona-warning app, simply permits all actions to
all actors in both locations.
\begin{ttbox}
  local_policies G \ttequiv
         (\ttlam x. if x = pub then  \{(\ttlam y. True, \{get,move,put\})\}
          else (if x = shop then \{(\ttlam y. True, \{get,move,put\})\} else \{\}))
\end{ttbox}  
For the Corona-warning app, the initial infrastructure contains the graph \texttt{ex\_graph}
with its two locations pub and shop and is then wrapped up with the local policies
into the infrastructure \texttt{Corona\_scenario} 
that represents the ``initial'' state for the Kripke structure.
\begin{ttbox}
 Corona_scenario \ttequiv Infrastructure  ex_graph local_policies
\end{ttbox}

\subsection{Policies, privacy, and behaviour}
\label{sec:}
Policies specify the expected behaviour of actors of an infrastructure. 
They are given by pairs of predicates (conditions) and sets of (enabled) actions.
%\begin{ttbox}
%{\bf type}_{\bf{synonym}} policy = ((actor \ttfun bool) \tttimes action set)
%\end{ttbox}
%The behaviour of actors is 
They are defined by the \texttt{enables} predicate:
an actor \texttt{h} is enabled to perform an action \texttt{a} 
in infrastructure \texttt{I}, at location \texttt{l}
if there exists a pair \texttt{(p,e)} in the local policy of \texttt{l}
(\texttt{delta I l} projects to the local policy) such that the action 
\texttt{a} is a member of the action set \texttt{e} and the policy 
predicate \texttt{p} holds for actor \texttt{h}.
\begin{ttbox}
enables I l h a \ttequiv \ttexists (p,e) \ttin delta I l. a \ttin e \ttand p h
\end{ttbox}

The Privacy protection goal is to avoid deanonymisation. That is, an attacker should not be able to
disambiguate the set of pairs of real Ids and EphIds. This is abstractly expressed in the predicate
identifiable.
\begin{ttbox}
identifiable eid A \ttequiv is_singleton\{(Id,Eid). (Id, Eid) \ttin A \ttand Eid = eid\}
\end{ttbox}
The predicate identifiable is used to express as the global policy `Eve cannot deanonymize an Ephemeral
Id \texttt{eid} using the gathered knowledge':
%{\bf fixes} global_policy::[infrastructure, identity] \ttfun bool
%{\bf defines}  
\begin{ttbox}
  global_policy I eid \ttequiv
             \ttneg(identifiable eid 
                ((\ttbigcap (kgra(graphI I)(Actor ''Eve'')`(nodes(graphI I))))
                 - \{(x,y). x = ''Eve''\}))
\end{ttbox}

\subsection{Infrastructure state transition}
\label{sec:statetrans}
The state transition relation uses the syntactic infix notation 
\texttt{I \ttrelI\, I'}  to denote that infrastructures 
\texttt{I} and \texttt{I'} are in this relation.
%Rules for the put, get, move, process and delete actions exist.
To give an impression of this definition, we show first the rule defining the state transition for
the action get. Initially, this rule expresses that
an actor that resides at a location \texttt{l} (\texttt{a \ttatI\ l})
and is enabled by the local policy in this location to ``get'' can
combine  all ids at the current location (contained in \texttt{egra G l}) with
all actors at the current location (contained in \texttt{agra G l}) and add this
set of pairs to his knowledge set \texttt{kgra G} using the function update \texttt{f(l := n)}
redefining the function \texttt{f} for the input \texttt{l} to have now the new value \texttt{n}.
\begin{ttbox}
 {\bf{get\_data}}: G = graphI I \ttImp a \ttatI l \ttImp enables I l (Actor a) get \ttImp 
   I' = Infrastructure 
          (Lgraph (gra G)(agra G)(cgra G)(lgra G)(egra G)
            ((kgra G)((Actor a) := ((kgra G (Actor a))(l:=
                 \{(x,y). x \ttin agra G l \ttand y \ttin egra G l\})))))
          (delta I)
   \ttImp I \ttrel{n} I' 
\end{ttbox}
Another interesting rule for the state transition is the one for \texttt{move} whose structure
resembles the previous one.
\begin{ttbox}
 {\bf{move}}: G = graphI I \ttImp  a \ttin actors_graph(graphI I) \ttImp
    l \ttin nodes G \ttImp l' \ttin nodes G \ttImp enables I l' (Actor h) move \ttImp
    I' = Infrastructure (move_graph_a a l l' (graphI I))(delta I)
 \ttImp I \ttrelI I' 
\end{ttbox}
The semantics of this rule is embedded in the function \texttt{move\_graph\_a}
that adapts the infrastructure state so that the moving actor \texttt{a} is now
associated to the target location \texttt{l'} in the actor map \texttt{agra} and not
any more at \texttt{l} and also the association of \texttt{efids} is updated accordingly.
\begin{ttbox}
move_graph_a n l l' g \ttequiv
  Lgraph (gra g) 
         (if n \ttin ((agra g) l) \ttand  n \ttnin ((agra g) l') then 
           ((agra g)(l := (agra g l) - \{n\}))(l' := (insert n (agra g l')))
          else (agra g))
         (cgra g)(lgra g)
         (if n \ttin ((agra g) l) \ttand  n \ttnin ((agra g) l') then
               ((egra g)(l := (egra g l) - \{efemid (cgra g n)\}))
                        (l' := (insert (efemid (cgra g n))(egra g l')))
          else egra g)
         (kgra g)
\end{ttbox}  
Based on this state transition and the above defined \texttt{Corona\_scenario}, we define the first Kripke structure.
\begin{ttbox}
 corona_Kripke \ttequiv Kripke \{ I. Corona_scenario \ttrelIstar I \} \{Corona_scenario\}
\end{ttbox}

\subsection{Attack analysis}
\label{sec:ana}
For the analysis of attacks, we negate the security property that we want to achieve,
usually the global policy.

Since we consider a predicate transformer semantics, we use
sets of states to represent properties. 
%For example, the attack property
The invalidated global policy is given by the following set \texttt{shc}.
\begin{ttbox}
 scorona \ttequiv \{x. \ttexists n. \ttneg global_policy x (Efid n)\}
\end{ttbox}
The attack we are interested in is to see whether for the scenario
\begin{ttbox}
 Kripke\_scenario \ttequiv  Infrastructure ex_graph local_policies 
\end{ttbox}
from the initial state \texttt{Icorona \ttequiv \{corona\_scenario\}},
the critical state \texttt{scorona} can be reached,
that is, is there a valid attack \texttt{(Icorona,scorona)}?

For the Kripke structure \texttt{corona\_Kripke}
we first derive a valid and-attack using the attack tree proof calculus.
\begin{ttbox}
  \ttvdash [\ttcalN{(Icorona,Corona)},\ttcalN{(Corona,Corona1)},\ttcalN{(Corona1,Corona2)},
             \ttcalN{(Corona2,Corona3)},\ttcalN{(Corona3,scorona)}]\ttattand{\texttt{(Icorona,scorona)}}
\end{ttbox}
The sets \texttt{Corona, Corona1, Corona2, Corona3} are the intermediate states where
\texttt{Bob} moves to shop and \texttt{Eve} follows him collecting the Ephemeral Ids in each location.
The collected information enables to identify Bob's Ephemeral Id.

The attack tree calculus \cite{kam:18b} exhibits that an attack is possible.
\begin{ttbox}
 corona_Kripke \ttvdash {\sf EF} scorona
\end{ttbox}
We can simply apply the Correctness theorem \texttt{AT\_EF} to 
immediately prove this CTL statement. This application of the meta-theorem 
of Correctness of attack trees saves us proving the CTL formula tediously 
by exploring the state space in Isabelle proofs. Alternatively, we could use 
the generated code for the function \texttt{is\_attack\_tree} in Scala 
(see Section \ref{sec:at}) to check that a refined attack of the above is valid.

@@

\subsection{Refining the Specification}
\label{sec:corref}
